# Study 1

**Create a dataset with data from Study 1**
```{r}
Data_Study1_Wide<-Data_Study1_Raw %>% filter(CCA==1 & Attention_check==1)
```

**Transform the data in long format to run GEE**
```{r results='hide', message=FALSE, warning=FALSE}
Data_Study1_Long<-Data_Study1_Wide %>% 
  pivot_longer(
    c(
       "Submarine_1", 
       "Trespassers_1", 
       "Hostages_1", 
       "Liferaft_1", 
       "PlaneCrash_1", 
       "PrisWar_1", 
       "Spelunkers_1", 
       "Soldier_1", 
       "Surgery_1", 
       "Footbridge_1", 
       "Cryingbaby_1"), 
    names_to = "Scenario", values_to = "Moral")

Data_Study1_Long$Trial<-rep(1:11, times=length(Data_Study1_Wide$Age))
```

## Data analysis
**Run Generalized Estimating Equations (GEE) for each sleep variable (IV) on moral judgments (DV)**
```{r}
GEE_SleepQualCroS1 <- geeglm(Moral~SleepQualCro, family=gaussian, id=ResponseId, corstr="exchangeable", Data_Study1_Long)
GEE_SleepQualAcuS1 <- geeglm(Moral~SleepQualAcu, family=gaussian, id=ResponseId, corstr="exchangeable", Data_Study1_Long)
GEE_SleepQuantCroS1 <- geeglm(Moral~SleepQuantCro, family=gaussian, id=ResponseId, corstr="exchangeable", Data_Study1_Long)
GEE_SleepQuantAcuS1 <- geeglm(Moral~SleepQuantAcu, family=gaussian, id=ResponseId, corstr="exchangeable", Data_Study1_Long)
```

**Extract coefficients from GEE models **
```{r}
results_S1 <- rbind(
  tidy(GEE_SleepQualCroS1)[2,],
  tidy(GEE_SleepQualAcuS1)[2,],
  tidy(GEE_SleepQuantCroS1)[2,],
  tidy(GEE_SleepQuantAcuS1)[2,]) %>%
  mutate(
    p.value = case_when(
      p.value*4 < 1 ~ p.value*4,
      p.value*4 >= 1 ~ 1))
```

**Prepare data for plots**
```{r}
Data_PlotS1<- Data_Study1_Wide %>%
  pivot_longer(
    cols=c(SleepQualCro, SleepQualAcu, SleepQuantCro, SleepQuantAcu),
    names_to="SleepType") %>%
  rename("SleepValue"=value) %>%
  mutate(
    SleepLength=case_when(
      SleepType=="SleepQualCro" | SleepType=="SleepQuantCro"~"Chronic",
      SleepType=="SleepQualAcu" | SleepType=="SleepQuantAcu"~"Acute"),
    SleepQuanthist=case_when(
      SleepType=="SleepQualCro" | SleepType=="SleepQualAcu"~"Sleep Quality",
      SleepType=="SleepQuantCro" | SleepType=="SleepQuantAcu"~"Sleep Quantity"))

Data_PlotS1$SleepType<-dplyr::recode(Data_PlotS1$SleepType, 
        "SleepQualCro" = "Quality of Chronic Sleep",
        "SleepQualAcu" = "Quality of Acute Sleep",
        "SleepQuantCro" = "Quantity of Chronic Sleep",
        "SleepQuantAcu" = "Quantity of Acute Sleep")
```

## Summary of Study 1 results 

**Put results in a table**
```{r}
gt(results_S1) %>% 
  fmt_number(
    columns = 2:5,
    decimals = 2)
```


## Plot Study 1 results

**Plot distribution for each sleep indicator**
```{r}
DistQualityS1<-ggplot(Data_PlotS1, aes(x=SleepValue, fill=SleepLength)) + 
  geom_density(alpha=0.5, size=0.5,adjust = 2) + 
  scale_fill_manual(values=c("#193B94", "#BDCAEE", "#193B94", "#BDCAEE")) +
  theme_bw() + 
  ylab("Density") + xlab("") +
  facet_wrap(~SleepQuanthist, scale="free_x") + 
  guides(fill=guide_legend("Sleep Length")) +
  theme(
    axis.title.y = element_text(size = 11, hjust = 0.5, face="bold"),
    axis.title.x = element_text(face="bold", size = 11, hjust = 0.5),
    legend.position="top",
    legend.title = element_text(colour="black", size=10, face="bold")) 

DistQualityS1
```

**Plot distribution of the scores to the sacrificial dilemmas**
```{r}
DistMoralS1<-ggplot(Data_Study1_Raw, aes(x=Moral_DIL, fill="#193B94")) + 
  geom_density(alpha=0.5, size=0.5,adjust = 2) + 
  theme_bw() + 
  ylab("Density") + xlab("Sacrificial Dilemmas") +
  guides(fill="none") +
  theme(
    axis.title.y = element_text(size = 11, hjust = 0.5, face="bold"),
    axis.title.x = element_text(face="bold", size = 11, hjust = 0.5))
  
DistMoralS1
```


**Scatterplots**
```{r}
ggplot(Data_PlotS1, aes(x=SleepValue, y=Moral_DIL)) + 
       geom_jitter(alpha=0.6, color="#545454", size=1.2) + 
       geom_smooth(method="lm") +
       facet_wrap(~SleepType, nrow = 2, ncol = 2, scales="free_x") +
       theme_bw() + ylab("Utilitirianism") + xlab("") + 
       theme(axis.title.y = element_text(size = 11, hjust = 0.5, face="bold"), 
             axis.title.x = element_text(face="bold", size = 11, hjust = 0.5)) +
       guides(size=FALSE, colour=FALSE, fill=FALSE)
```