# Study 2

```{r}
Data_Study2_Wide<-Data_Meta_Raw.wide[Data_Meta_Raw.wide$Study==2,]
```

## Data analysis
**Run linear regressions for each sleep variable (IV) on endorsement of moral principles (DV)**
```{r}
QualCroLMS2<-lm(Moral_SCA~SleepQualCro, Data_Study2_Wide)
QualAcuLMS2<-lm(Moral_SCA~SleepQualAcu,Data_Study2_Wide)
QuantCroLMS2<-lm(Moral_SCA~SleepQuantCro, Data_Study2_Wide)
QuantAcuLMS2<-lm(Moral_SCA~SleepQuantAcu, Data_Study2_Wide)
```

**Extract coefficients (unstandardized slopes, standard errors and p-values) from linear regression models **
```{r}
#Chronic Sleep Quality
bQualCroS2<-round(summary(QualCroLMS2)$coefficients[2,1], digit=2)
SEQualCroS2<- round(summary(QualCroLMS2)$coefficients[2,2] , digit=2)
pQualCroS2<- round(ifelse(summary(QualCroLMS2)$coefficients[2,4]*4<.99, summary(QualCroLMS2)$coefficients[2,4]*4, .99), digit=2)

#Acute Sleep Quality
bQualAcuS2<- round(summary(QualAcuLMS2)$coefficients[2,1] , digit=2)
SEQualAcuS2 <- round(summary(QualAcuLMS2)$coefficients[2,2] , digit=2)
pQualAcuS2<- round(ifelse(summary(QualAcuLMS2)$coefficients[2,4]*4<.99, summary(QualAcuLMS2)$coefficients[2,4]*4, .99), digit=2)

#Chronic Sleep Quantity
bQuantCroS2<- round(summary(QuantCroLMS2)$coefficients[2,1] , digit=2)
SEQuantCroS2 <- round(summary(QuantCroLMS2)$coefficients[2,2] , digit=2)
pQuantCroS2<- round(ifelse(summary(QuantCroLMS2)$coefficients[2,4]*4<.99, summary(QuantCroLMS2)$coefficients[2,4]*4, .99), digit=2)

#Acute Sleep Quantity
bQuantAcuS2<- round(summary(QuantAcuLMS2)$coefficients[2,1] , digit=2)
SEQuantAcuS2 <- round(summary(QuantAcuLMS2)$coefficients[2,2] , digit=2)
pQuantAcuS2<- round(ifelse(summary(QuantAcuLMS2)$coefficients[2,4]*4<.99, summary(QuantAcuLMS2)$coefficients[2,4]*4, .99), digit=2)

```

**Create datasets to display regression summary in plots**
```{r}
ResumQualCroS2<- paste0("b=",bQualCroS2,", ", "SE=",SEQualCroS2,", ","p=",pQualCroS2)
ResumQualAcuS2<- paste0("b=",bQualAcuS2,", ", "SE=",SEQualAcuS2,", ","p=",pQualAcuS2)
ResumQuantCroS2<- paste0("b=",bQuantCroS2,", ", "SE=",SEQuantCroS2,", ","p=",pQuantCroS2)
ResumQuantAcuS2<- paste0("b=",bQuantAcuS2,", ", "SE=",SEQuantAcuS2,", ","p=",pQuantAcuS2)

annotationQualCroS2 <- data.frame(x = 5, y = 45,  label = ResumQualCroS2)
annotationQualAcuS2 <- data.frame(x = 5, y = 45,  label = ResumQualAcuS2)
annotationQuantCroS2 <- data.frame(x =5, y = 45,  label = ResumQuantCroS2)
annotationQuantAcuS2 <- data.frame(x = 5, y = 45,  label = ResumQuantAcuS2)

annotationS2<-cbind(
  rbind(annotationQualCroS2, 
        annotationQualAcuS2, 
        annotationQuantCroS2, 
        annotationQuantAcuS2),
  SleepType=c(
        "Quality of Chronic Sleep", 
        "Quality of Acute Sleep", 
        "Quantity of Chronic Sleep", 
        "Quantity of Acute Sleep"))
```


**Prepare data for plots**
```{r}
Data_PlotS2<- Data_Study2_Wide %>%
  pivot_longer(
    cols=c(SleepQualCro, SleepQualAcu, SleepQuantCro, SleepQuantAcu),
    names_to="SleepType") %>%
  rename("SleepValue"=value) %>%
  mutate(
    SleepLength=case_when(
      SleepType=="SleepQualCro" | SleepType=="SleepQuantCro"~"Chronic",
      SleepType=="SleepQualAcu" | SleepType=="SleepQuantAcu"~"Acute"),
    SleepQuanthist=case_when(
      SleepType=="SleepQualCro" | SleepType=="SleepQualAcu"~"Sleep Quality",
      SleepType=="SleepQuantCro" | SleepType=="SleepQuantAcu"~"Sleep Quantity"))

Data_PlotS2$SleepType<-dplyr::recode(Data_PlotS2$SleepType, 
        "SleepQualCro" = "Quality of Chronic Sleep",
        "SleepQualAcu" = "Quality of Acute Sleep",
        "SleepQuantCro" = "Quantity of Chronic Sleep",
        "SleepQuantAcu" = "Quantity of Acute Sleep")

```

**N in each sleep quantity category**
```{r}
Dist.Quantity.ChronicS2<-Data_Study2_Wide %>% 
    dplyr::group_by(SleepQuantCro) %>% 
      summarise(
        N=n()) %>% 
          spread(SleepQuantCro, N) %>% 
  as.data.frame()
row.names(Dist.Quantity.ChronicS2)<-"Quantity Chronic"

Dist.Quantity.AcuteS2<-Data_Study2_Wide %>% 
    dplyr::group_by(SleepQuantAcu) %>% 
      summarise(
        N=n()) %>% 
          spread(SleepQuantAcu, N) %>% 
  as.data.frame()
row.names(Dist.Quantity.AcuteS2)<-"Quantity Acute"

bind_rows(Dist.Quantity.AcuteS2, Dist.Quantity.ChronicS2)

```

## Summary of Study 2 results

**Put results in a table**
```{r}
SleepMarker<-c("Quality Chronic","Quality Acute","Quantity Chronic","Quantity Acute")
bS2<-c(bQualCroS2,bQualAcuS2,bQuantCroS2,bQuantAcuS2)
SES2<-c(SEQualCroS2,SEQualAcuS2,SEQuantCroS2,SEQuantAcuS2)
pvalS2<-c(pQualCroS2,pQualAcuS2,pQuantCroS2,pQuantAcuS2)
NS2<-c(length(QualCroLMS2$fitted.values),
     length(QualAcuLMS2$fitted.values),
     length(QuantCroLMS2$fitted.values),
     length(QuantAcuLMS2$fitted.values))
ResultsStudy2<-data.frame("Sleep Indicator"=SleepMarker, "Unstandardized Slope"=bS2, "Standard Errors"=SES2, "p values"=pvalS2, "N"=NS2)
gt(ResultsStudy2)
```

## Plot Study 2 Results

**Plot distribution for each sleep indicator**
```{r}
DistQualityS2<-ggplot(Data_PlotS2, aes(x=SleepValue, fill=factor(SleepLength))) + 
  geom_density(alpha=0.5, size=0.5,adjust = 2) + 
  scale_fill_manual(values=c("#193B94", "#BDCAEE", "#193B94", "#BDCAEE")) +
  theme_bw() + 
  ylab("Density") + xlab("") +
  facet_wrap(~factor(SleepQuanthist), scale="free_x") + 
  guides(fill=guide_legend("Sleep Length")) +
  theme(
    axis.title.y = element_text(size = 11, hjust = 0.5, face="bold"),
    axis.title.x = element_text(face="bold", size = 11, hjust = 0.5),
    legend.position="top",
    legend.title = element_text(colour="black", size=10, face="bold")) 
DistQualityS2
```

**Plot distribution for the scores to the moral scale**
```{r}
DistMoralS2<-ggplot(Data_Study2_Raw, aes(x=Moral_SCA, fill="#193B94")) + 
  geom_density(alpha=0.5, size=0.5,adjust = 2) + 
  theme_bw() + 
  ylab("Density") + xlab("Moral Scale") +
  guides(fill="none") +
  theme(
    axis.title.y = element_text(size = 11, hjust = 0.5, face="bold"),
    axis.title.x = element_text(face="bold", size = 11, hjust = 0.5))
  
DistMoralS2
```

**Scatterplots**
```{r}
ggplot(Data_PlotS2, aes(x=SleepValue, y=Moral_SCA)) + 
       geom_jitter(alpha=0.6, color="#545454", size=1.2) + 
       # geom_line(aes(y= fit), colour="#0019D0", size=1.2) + 
       # geom_ribbon( aes(ymin = lwr, ymax = upr), fill = "#697BFC", alpha = .3)+
       geom_smooth(method="lm")+
       facet_wrap(~factor(SleepType), scales="free_x") +
       theme_bw() + ylab("Utilitirianism") + xlab("") + 
       theme(axis.title.y = element_text(size = 11, hjust = 0.5, face="bold"), 
             axis.title.x = element_text(face="bold", size = 11, hjust = 0.5)) +
       guides(size=FALSE, colour=FALSE, fill=FALSE) + 
       geom_label(data=annotationS2, aes( x=x, y=y, label=label), 
                  color="black",  size=3.5 , angle=45, alpha=7/10, inherit.aes = FALSE)
```