# Study 4
```{r}
Data_Study4_Wide<-Data_Meta_Raw.wide[Data_Meta_Raw.wide$Study==4,]
```

## Data analysis

**Planned statistical analysis: Run SEM for each sleep variable (IV) on endorsement of moral principles (DV)**
```{r}
#Primary Analysis
Model_QualCroSEMS4<-
'MoralTOT=~Moral_DIL+Moral_SCA+Moral_CAR
MoralTOT~SleepQualCro'
fitQualCro<-sem(Model_QualCroSEMS4, data=Data_Study4_Wide, estimator="MLR")

#Secondary Analyses
Model_QualAcuSEMS4<-
'MoralTOT=~Moral_DIL+Moral_SCA+Moral_CAR
MoralTOT~SleepQualAcu'
fitQualAcu<-sem(Model_QualAcuSEMS4, data=Data_Study4_Wide, estimator="MLR")


Model_QuantCroSEMS4<-
'MoralTOT=~Moral_DIL+Moral_SCA+Moral_CAR
MoralTOT~SleepQuantCro'
fitQuantCro<-sem(Model_QuantCroSEMS4, data=Data_Study4_Wide, estimator="MLR")


Model_QuantAcuSEMS4<-
'MoralTOT=~Moral_DIL+Moral_SCA+Moral_CAR
MoralTOT~SleepQuantAcu'
fitQuantAcu<-sem(Model_QuantAcuSEMS4, data=Data_Study4_Wide, estimator="MLR")


summary(fitQualCro)
summary(fitQualAcu)
summary(fitQuantCro)
summary(fitQualCro)

```

**Alternative statistical analysis: using a composite variable as the dependent variable instead of a latent variable**
```{r}
# creation of the composite variable
Data_Study4_Wide$MoralZ_DIL<- scale(Data_Study4_Wide$Moral_DIL,
                                   center = TRUE, scale = TRUE)

Data_Study4_Wide$MoralZ_SCA<- scale(Data_Study4_Wide$Moral_SCA,
                                   center = TRUE, scale = TRUE)

Data_Study4_Wide$MoralZ_CAR<- scale(Data_Study4_Wide$Moral_CAR,
                                   center = TRUE, scale = TRUE)

Data_Study4_Wide$MoralZ<-with(Data_Study4_Wide, MoralZ_DIL+MoralZ_SCA+MoralZ_CAR)

# univariate regression
QualCroLMS4<-lm(MoralZ~SleepQualCro, Data_Study4_Wide)
QualAcuLMS4<-lm(MoralZ~SleepQualAcu, Data_Study4_Wide)
QuantCroLMS4<-lm(MoralZ~SleepQuantCro,Data_Study4_Wide)
QuantAcuLMS4<-lm(MoralZ~SleepQuantAcu, Data_Study4_Wide)
```


**Extract coefficients (unstandardized slopes, standard errors and p-values) from linear regression models **
```{r}
#Chronic Sleep Quality
bQualCroS4<-round(summary(QualCroLMS4)$coefficients[2,1], digit=2)
SEQualCroS4<- round(summary(QualCroLMS4)$coefficients[2,2] , digit=2)
pQualCroS4<- round(summary(QualCroLMS4)$coefficients[2,4], digit=2)

#Acute Sleep Quality
bQualAcuS4<- round(summary(QualAcuLMS4)$coefficients[2,1] , digit=2)
SEQualAcuS4 <- round(summary(QualAcuLMS4)$coefficients[2,2] , digit=2)
pQualAcuS4<- round(ifelse(summary(QualAcuLMS4)$coefficients[2,4]*3<.99, summary(QualAcuLMS4)$coefficients[2,4]*3, .99), digit=2)

#Chronic Sleep Quantity
bQuantCroS4<- round(summary(QuantCroLMS4)$coefficients[2,1] , digit=2)
SEQuantCroS4 <- round(summary(QuantCroLMS4)$coefficients[2,2] , digit=2)
pQuantCroS4<- round(ifelse(summary(QuantCroLMS4)$coefficients[2,4]*4<.99, summary(QuantCroLMS4)$coefficients[2,4]*3, .99), digit=2)

#Acute Sleep Quantity
bQuantAcuS4<- round(summary(QuantAcuLMS4)$coefficients[2,1] , digit=2)
SEQuantAcuS4 <- round(summary(QuantAcuLMS4)$coefficients[2,2] , digit=2)
pQuantAcuS4<- round(ifelse(summary(QuantAcuLMS4)$coefficients[2,4]*3<.99, summary(QuantAcuLMS4)$coefficients[2,4]*3, .99), digit=2)

```

**Create datasets to display regression summary on the plots**
```{r}
ResumQualCroS4<- paste0("b=",bQualCroS4,", ", "SE=",SEQualCroS4,", ","p=",pQualCroS4)
ResumQualAcuS4<- paste0("b=",bQualAcuS4,", ", "SE=",SEQualAcuS4,", ","p=",pQualAcuS4)
ResumQuantCroS4<- paste0("b=",bQuantCroS4,", ", "SE=",SEQuantCroS4,", ","p=",pQuantCroS4)
ResumQuantAcuS4<- paste0("b=",bQuantAcuS4,", ", "SE=",SEQuantAcuS4,", ","p=",pQuantAcuS4)

annotationQualCroS4 <- data.frame(x = 9, y = 5.5,  label = ResumQualCroS4)
annotationQualAcuS4 <- data.frame(x = 6, y = 5.5,  label = ResumQualAcuS4)
annotationQuantCroS4 <- data.frame(x =6, y = 5.5,  label = ResumQuantCroS4)
annotationQuantAcuS4 <- data.frame(x = 6, y = 5.5,  label = ResumQuantAcuS4)

annotationS4<-cbind(
  rbind(annotationQualCroS4,
        annotationQualAcuS4,
        annotationQuantCroS4,
        annotationQuantAcuS4),
  SleepType=c(
        "Quality of Chronic Sleep",
        "Quality of Acute Sleep",
        "Quantity of Chronic Sleep",
        "Quantity of Acute Sleep"))
```


**Prepare data for plots**
```{r}
Data_PlotS4<- Data_Study4_Wide %>%
  pivot_longer(
    cols=c(SleepQualCro, SleepQualAcu, SleepQuantCro, SleepQuantAcu),
    names_to="SleepType") %>%
  rename("SleepValue"=value) %>%
  mutate(
    SleepLength=case_when(
      SleepType=="SleepQualCro" | SleepType=="SleepQuantCro"~"Chronic",
      SleepType=="SleepQualAcu" | SleepType=="SleepQuantAcu"~"Acute"),
    SleepQuanthist=case_when(
      SleepType=="SleepQualCro" | SleepType=="SleepQualAcu"~"Sleep Quality",
      SleepType=="SleepQuantCro" | SleepType=="SleepQuantAcu"~"Sleep Quantity"))

Data_PlotS4$SleepType<-dplyr::recode(Data_PlotS4$SleepType,
        "SleepQualCro" = "Quality of Chronic Sleep",
        "SleepQualAcu" = "Quality of Acute Sleep",
        "SleepQuantCro" = "Quantity of Chronic Sleep",
        "SleepQuantAcu" = "Quantity of Acute Sleep")


Data_MoralS4<- Data_Study4_Wide %>%
  pivot_longer(
    cols=c(Moral_DIL, Moral_SCA, Moral_CAR),
    names_to="Outcome_moral") %>%
  rename("MoralValue"=value)

Data_MoralS4$Outcome_moral<-dplyr::recode(Data_MoralS4$Outcome_moral,
        "Moral_DIL" = "Dilemmas",
        "Moral_SCA" = "Scale",
        "Moral_CAR" = "Autonomous cars")
```


**N in each sleep quantity category**
```{r}
Dist.Quantity.ChronicS4<-Data_Study4_Wide %>%
    dplyr::group_by(SleepQuantCro) %>%
      summarise(
        N=n()) %>%
          spread(SleepQuantCro, N) %>%
  as.data.frame()
row.names(Dist.Quantity.ChronicS4)<-"Quantity Chronic"

Dist.Quantity.AcuteS4<-Data_Study4_Wide %>%
    dplyr::group_by(SleepQuantAcu) %>%
      summarise(
        N=n()) %>%
          spread(SleepQuantAcu, N) %>%
  as.data.frame()
row.names(Dist.Quantity.AcuteS4)<-"Quantity Acute"

bind_rows(Dist.Quantity.AcuteS4, Dist.Quantity.ChronicS4)

```

## Summary of Study 4 results

**Put results in a table**
```{r}
SleepMarker<-c("Quality Chronic","Quality Acute","Quantity Chronic","Quantity Acute")
bS4<-c(bQualCroS4,bQualAcuS4,bQuantCroS4,bQuantAcuS4)
SES4<-c(SEQualCroS4,SEQualAcuS4,SEQuantCroS4,SEQuantAcuS4)
pvalS4<-c(pQualCroS4,pQualAcuS4,pQuantCroS4,pQuantAcuS4)
NS4<-c(length(QualCroLMS4$fitted.values),
     length(QualAcuLMS4$fitted.values),
     length(QuantCroLMS4$fitted.values),
     length(QuantAcuLMS4$fitted.values))

ResultsStudy4<-data.frame("Sleep Indicator"=SleepMarker, "Unstandardized Slope"=bS4, "Standard Errors"=SES4, "p values"=pvalS4, "N"=NS4)
gt(ResultsStudy4)
```

## Plots of Study 4 results

**Plot distribution for each sleep indicator**
```{r}
DistQualityS4<-ggplot(Data_PlotS4, aes(x=SleepValue, fill=factor(SleepLength))) +
  geom_density(alpha=0.5, size=0.5,adjust = 2) +
  scale_fill_manual(values=c("#193B94", "#BDCAEE", "#193B94", "#BDCAEE")) +
  theme_bw() +
  ylab("Density") + xlab("") +
  facet_wrap(~factor(SleepQuanthist), scale="free_x") +
  guides(fill=guide_legend("Sleep Length")) +
  theme(
    axis.title.y = element_text(size = 11, hjust = 0.5, face="bold"),
    axis.title.x = element_text(face="bold", size = 11, hjust = 0.5),
    legend.position="top",
    legend.title = element_text(colour="black", size=10, face="bold"))
DistQualityS4
```

**Plot distribution for the scores to the sacrificial dilemmas, moral scale and autonomous car dilemmas**
```{r}
DistMoralS4<-ggplot(Data_MoralS4, aes(x=MoralValue, fill=factor(Outcome_moral))) + 
  geom_density(alpha=0.5, size=0.5,adjust = 2) + 
  theme_bw() + 
  ylab("Density") + xlab("Moral Scale") +
  facet_wrap(~factor(Outcome_moral), scale="free") +
  guides(fill="none") +
  theme(
    axis.title.y = element_text(size = 11, hjust = 0.5, face="bold"),
    axis.title.x = element_text(face="bold", size = 11, hjust = 0.5))
  
DistMoralS4
```

**Scatterplots**
```{r}
ggplot(Data_PlotS4, aes(x=SleepValue, y=MoralZ)) +
       geom_jitter(alpha=0.6, color="#545454", size=1.2) +
       geom_smooth(method="lm")+
       facet_wrap(~factor(SleepType), scales="free_x") +
       theme_bw() + ylab("Utilitirianism") + xlab("") +
       theme(axis.title.y = element_text(size = 11, hjust = 0.5, face="bold"),
             axis.title.x = element_text(face="bold", size = 11, hjust = 0.5)) +
       guides(size=FALSE, colour=FALSE, fill=FALSE) +
       geom_label(data=annotationS4, aes( x=x, y=y, label=label),
                  color="black",  size=3.5 , angle=45, alpha=7/10, inherit.aes = FALSE)
```