# Study 4
```{r}
Data_Study4_Wide <- subset(Data_Meta_Raw.wide, Study == 4)
```

## Data analysis

**Planned statistical analysis: Run SEM for each sleep variable (IV) on endorsement of moral principles (DV)**
```{r}
#Primary Analysis
Model_QualCroSEMS4<-
'MoralTOT=~Moral_DIL+Moral_SCA+Moral_CAR
MoralTOT~SleepQualCro'
fitQualCro<-sem(Model_QualCroSEMS4, data=Data_Study4_Wide, estimator="MLR")

#Secondary Analyses
Model_QualAcuSEMS4<-
'MoralTOT=~Moral_DIL+Moral_SCA+Moral_CAR
MoralTOT~SleepQualAcu'
fitQualAcu<-sem(Model_QualAcuSEMS4, data=Data_Study4_Wide, estimator="MLR")


Model_QuantCroSEMS4<-
'MoralTOT=~Moral_DIL+Moral_SCA+Moral_CAR
MoralTOT~SleepQuantCro'
fitQuantCro<-sem(Model_QuantCroSEMS4, data=Data_Study4_Wide, estimator="MLR")


Model_QuantAcuSEMS4<-
'MoralTOT=~Moral_DIL+Moral_SCA+Moral_CAR
MoralTOT~SleepQuantAcu'
fitQuantAcu<-sem(Model_QuantAcuSEMS4, data=Data_Study4_Wide, estimator="MLR")


summary(fitQualCro)
summary(fitQualAcu)
summary(fitQuantCro)
summary(fitQualCro)

```

**Alternative statistical analysis: using a composite variable as the dependent variable instead of a latent variable**
```{r}
# creation of the composite variable
Data_Study4_Wide$MoralZ_DIL<- scale(Data_Study4_Wide$Moral_DIL,
                                   center = TRUE, scale = TRUE)

Data_Study4_Wide$MoralZ_SCA<- scale(Data_Study4_Wide$Moral_SCA,
                                   center = TRUE, scale = TRUE)

Data_Study4_Wide$MoralZ_CAR<- scale(Data_Study4_Wide$Moral_CAR,
                                   center = TRUE, scale = TRUE)

Data_Study4_Wide$MoralZ<-with(Data_Study4_Wide, MoralZ_DIL+MoralZ_SCA+MoralZ_CAR)

# univariate regression
QualCroLMS4<-lm(MoralZ~SleepQualCro, Data_Study4_Wide)
QualAcuLMS4<-lm(MoralZ~SleepQualAcu, Data_Study4_Wide)
QuantCroLMS4<-lm(MoralZ~SleepQuantCro,Data_Study4_Wide)
QuantAcuLMS4<-lm(MoralZ~SleepQuantAcu, Data_Study4_Wide)
```


**Extract coefficients from linear regression models **
```{r}
results_S4 <- rbind(
  tidy(QualCroLMS4)[2,],
  tidy(QualAcuLMS4)[2,],
  tidy(QuantCroLMS4)[2,],
  tidy(QuantAcuLMS4)[2,]) %>%
  mutate(
    p.value = case_when(
      p.value*4 < 1 ~ p.value*4,
      p.value*4 >= 1 ~ 1))
```

**Prepare data for plots**
```{r}
Data_PlotS4<- Data_Study4_Wide %>%
  pivot_longer(
    cols=c(SleepQualCro, SleepQualAcu, SleepQuantCro, SleepQuantAcu),
    names_to="SleepType") %>%
  rename("SleepValue"=value) %>%
  mutate(
    SleepLength=case_when(
      SleepType=="SleepQualCro" | SleepType=="SleepQuantCro"~"Chronic",
      SleepType=="SleepQualAcu" | SleepType=="SleepQuantAcu"~"Acute"),
    SleepQuanthist=case_when(
      SleepType=="SleepQualCro" | SleepType=="SleepQualAcu"~"Sleep Quality",
      SleepType=="SleepQuantCro" | SleepType=="SleepQuantAcu"~"Sleep Quantity"))

Data_PlotS4$SleepType<-dplyr::recode(Data_PlotS4$SleepType,
        "SleepQualCro" = "Quality of Chronic Sleep",
        "SleepQualAcu" = "Quality of Acute Sleep",
        "SleepQuantCro" = "Quantity of Chronic Sleep",
        "SleepQuantAcu" = "Quantity of Acute Sleep")


Data_MoralS4<- Data_Study4_Wide %>%
  pivot_longer(
    cols=c(Moral_DIL, Moral_SCA, Moral_CAR),
    names_to="Outcome_moral") %>%
  rename("MoralValue"=value)

Data_MoralS4$Outcome_moral<-dplyr::recode(Data_MoralS4$Outcome_moral,
        "Moral_DIL" = "Dilemmas",
        "Moral_SCA" = "Scale",
        "Moral_CAR" = "Autonomous cars")
```

## Summary of Study 4 results

**Put results in a table**
```{r}
gt(results_S4) %>% 
  fmt_number(
    columns = 2:5,
    decimals = 2)
```

## Plots of Study 4 results

**Plot distribution for each sleep indicator**
```{r}
DistQualityS4<-ggplot(Data_PlotS4, aes(x=SleepValue, fill=factor(SleepLength))) +
  geom_density(alpha=0.5, size=0.5,adjust = 2) +
  scale_fill_manual(values=c("#193B94", "#BDCAEE", "#193B94", "#BDCAEE")) +
  theme_bw() +
  ylab("Density") + xlab("") +
  facet_wrap(~factor(SleepQuanthist), scale="free_x") +
  guides(fill=guide_legend("Sleep Length")) +
  theme(
    axis.title.y = element_text(size = 11, hjust = 0.5, face="bold"),
    axis.title.x = element_text(face="bold", size = 11, hjust = 0.5),
    legend.position="top",
    legend.title = element_text(colour="black", size=10, face="bold"))
DistQualityS4
```

**Plot distribution for the scores to the sacrificial dilemmas, moral scale and autonomous car dilemmas**
```{r}
DistMoralS4<-ggplot(Data_MoralS4, aes(x=MoralValue, fill=factor(Outcome_moral))) + 
  geom_density(alpha=0.5, size=0.5,adjust = 2) + 
  theme_bw() + 
  ylab("Density") + xlab("Moral Scale") +
  facet_wrap(~factor(Outcome_moral), scale="free") +
  guides(fill="none") +
  theme(
    axis.title.y = element_text(size = 11, hjust = 0.5, face="bold"),
    axis.title.x = element_text(face="bold", size = 11, hjust = 0.5))
  
DistMoralS4
```

**Scatterplots**
```{r}
ggplot(Data_PlotS4, aes(x=SleepValue, y=MoralZ)) +
       geom_jitter(alpha=0.6, color="#545454", size=1.2) +
       geom_smooth(method="lm")+
       facet_wrap(~factor(SleepType), scales="free_x") +
       theme_bw() + ylab("Utilitirianism") + xlab("") +
       theme(axis.title.y = element_text(size = 11, hjust = 0.5, face="bold"),
             axis.title.x = element_text(face="bold", size = 11, hjust = 0.5)) +
       guides(size=FALSE, colour=FALSE, fill=FALSE) 
```