# Study 5

```{r}
Data_Study5_Wide <- subset(Data_Meta_Raw.wide, Study == 5)
```

## Data analysis

**Run a multivariate regression for each sleep variable (IV) on endorsement of moral principles assessed using moral dilemmas and a moral scale as DVs**
```{r}
QualCroLMS5<-lm(cbind(Moral_DIL, Moral_SCA)~SleepQualCro,Data_Study5_Wide)
QualAcuLMS5<-lm(cbind(Moral_DIL, Moral_SCA)~SleepQualAcu,Data_Study5_Wide)
QuantCroLMS5<-lm(cbind(Moral_DIL, Moral_SCA)~SleepQuantCro, Data_Study5_Wide)
QuantAcuLMS5<-lm(cbind(Moral_DIL, Moral_SCA)~SleepQuantAcu, Data_Study5_Wide)
```

**Extract coefficients (F test and p-values) from multivariate regression models **
```{r}
out <- car:::print.Anova.mlm
body(out)[[16]] <- quote(invisible(tests))
body(out)[[15]] <- NULL

#Chronic Sleep Quality
FQualCroS5<-round(do.call(rbind, out(Anova(QualCroLMS5, test.statistic="Pillai")))[3], digit=2)
pQualCroS5<-  round(ifelse(do.call(rbind, out(Anova(QualCroLMS5, test.statistic="Pillai")))[6]*4<.99, do.call(rbind, out(Anova(QualCroLMS5, test.statistic="Pillai")))[6]*4, .99), digit=2)

#Acute Sleep Quality
FQualAcuS5<-round(do.call(rbind, out(Anova(QualAcuLMS5, test.statistic="Pillai")))[3], digit=2)
pQualAcuS5<-  round(ifelse(do.call(rbind, out(Anova(QualAcuLMS5, test.statistic="Pillai")))[6]*4<.99, do.call(rbind, out(Anova(QualAcuLMS5, test.statistic="Pillai")))[6]*4, .99), digit=2)

#Chronic Sleep Quantity
FQuantCroS5<-round(do.call(rbind, out(Anova(QuantCroLMS5, test.statistic="Pillai")))[3], digit=2)
pQuantCroS5<-  round(ifelse(do.call(rbind, out(Anova(QuantCroLMS5, test.statistic="Pillai")))[6]*4<.99, do.call(rbind, out(Anova(QuantCroLMS5, test.statistic="Pillai")))[6]*4, .99), digit=2)

#Acute Sleep Quantity
FQuantAcuS5<-round(do.call(rbind, out(Anova(QuantCroLMS5, test.statistic="Pillai")))[3], digit=2)
pQuantAcuS5<-  round(ifelse(do.call(rbind, out(Anova(QuantAcuLMS5, test.statistic="Pillai")))[6]*4<.99, do.call(rbind, out(Anova(QuantAcuLMS5, test.statistic="Pillai")))[6]*4, .99), digit=2)

```

**Prepare data for plots**
```{r}
Data_PlotS5<- Data_Study5_Wide %>%
  pivot_longer(
    cols=c(SleepQualCro, SleepQualAcu, SleepQuantCro, SleepQuantAcu),
    names_to="SleepType") %>%
  rename("SleepValue"=value) %>%
  mutate(
    SleepLength=case_when(
      SleepType=="SleepQualCro" | SleepType=="SleepQuantCro"~"Chronic",
      SleepType=="SleepQualAcu" | SleepType=="SleepQuantAcu"~"Acute"),
    SleepQuanthist=case_when(
      SleepType=="SleepQualCro" | SleepType=="SleepQualAcu"~"Sleep Quality",
      SleepType=="SleepQuantCro" | SleepType=="SleepQuantAcu"~"Sleep Quantity"),
    MoralZ_DIL=scale(Moral_DIL, center = TRUE, scale = TRUE),
    MoralZ_SCA=scale(Moral_SCA, center = TRUE, scale = TRUE))

Data_PlotS5$SleepType<-dplyr::recode(Data_PlotS5$SleepType, 
        "SleepQualCro" = "Quality of Chronic Sleep",
        "SleepQualAcu" = "Quality of Acute Sleep",
        "SleepQuantCro" = "Quantity of Chronic Sleep",
        "SleepQuantAcu" = "Quantity of Acute Sleep")

Data_MoralS5<- Data_Study5_Wide %>%
  pivot_longer(
    cols=c(Moral_DIL, Moral_SCA),
    names_to="Outcome_moral") %>%
  rename("MoralValue"=value)

Data_MoralS5$Outcome_moral<-dplyr::recode(Data_MoralS5$Outcome_moral,
        "Moral_DIL" = "Dilemmas",
        "Moral_SCA" = "Scale")

Data_ScatterS5<- Data_PlotS5 %>%
  pivot_longer(
    cols=c(MoralZ_DIL, MoralZ_SCA),
    names_to="Outcome1") %>%
  rename("MoralValue1"=value)
Data_ScatterS5$Outcome<-dplyr::recode(Data_ScatterS5$Outcome, 
        "MoralZ_DIL" = "Dilemmas",
        "MoralZ_SCA" = "Scale")

```

## Summary of Study 5 results

**Put results in a table**
```{r}
SleepMarker<-c("Quality Chronic","Quality Acute","Quantity Chronic","Quantity Acute")
FS5<-c(FQualCroS5,FQualAcuS5,FQuantCroS5,FQuantAcuS5)
pvalS5<-c(pQualCroS5,pQualAcuS5,pQuantCroS5,pQuantAcuS5)
NS5<-c(length(QualCroLMS5$fitted.values)/2,
     length(QualAcuLMS5$fitted.values)/2,
     length(QuantCroLMS5$fitted.values)/2,
     length(QuantAcuLMS5$fitted.values)/2)
ResultsStudy5<-data.frame("Sleep Indicator"=SleepMarker, "F-test"=FS5, "p values"=pvalS5, "N"=NS5)
gt(ResultsStudy5)
```

## Plots of Study 5 results

**Plot distribution for each sleep indicator**
```{r}
DistQualityS5<-ggplot(Data_PlotS5, aes(x=SleepValue, fill=factor(SleepLength))) + 
  geom_density(alpha=0.5, size=0.5,adjust = 2) + 
  scale_fill_manual(values=c("#193B94", "#BDCAEE")) +
  theme_bw() + 
  ylab("Density") + xlab("") +
  facet_wrap(~factor(SleepQuanthist), scale="free_x") + 
  guides(fill=guide_legend("Sleep Length")) +
  theme(
    axis.title.y = element_text(size = 11, hjust = 0.5, face="bold"),
    axis.title.x = element_text(face="bold", size = 11, hjust = 0.5),
    legend.position="top",
    legend.title = element_text(colour="black", size=10, face="bold")) 
DistQualityS5
```

**Plot distribution for the scores to the dilemmas and moral scale**
```{r}
DistMoralS5<-ggplot(Data_MoralS5, aes(x=MoralValue, fill=factor(Outcome_moral))) + 
  geom_density(alpha=0.5, size=0.5,adjust = 2) + 
  theme_bw() + 
  ylab("Density") + xlab("Moral Scale") +
  facet_wrap(~factor(Outcome_moral), scale="free") +
  guides(fill="none") +
  theme(
    axis.title.y = element_text(size = 11, hjust = 0.5, face="bold"),
    axis.title.x = element_text(face="bold", size = 11, hjust = 0.5))
  
DistMoralS5
```

**Scatterplots**
```{r}
ggplot(Data_ScatterS5, aes(x=SleepValue, y=MoralValue1, 
                           color=Outcome1, fill=Outcome1)) + 
       geom_smooth(method="lm")+
      geom_point(alpha=0.2)+
       facet_wrap(~factor(SleepType), scales="free_x") +
       theme_bw() + ylab("Utilitirianism") + xlab("") + 
       theme(axis.title.y = element_text(size = 11, hjust = 0.5, face="bold"), 
             axis.title.x = element_text(face="bold", size = 11, hjust = 0.5)) +
       guides(size=FALSE, colour=FALSE) + 
       scale_fill_manual(values=c("red","#193B94"))+
       scale_color_manual(values=c("red","#193B94"))
```