# Study 6

```{r}
Data_Study6_Wide<-Data_Meta_Raw.wide[Data_Meta_Raw.wide$Study==6,]
```


## Data analysis

**Run a multivariate regression for each sleep variable (IV) on endorsement of moral principles assessed using moral dilemmas and a moral scale as DVs**
```{r}
QualCroLMS6<-lm(cbind(Moral_DIL, Moral_SCA)~SleepQualCro,Data_Study6_Wide)
QualAcuLMS6<-lm(cbind(Moral_DIL, Moral_SCA)~SleepQualAcu,Data_Study6_Wide)
QuantCroLMS6<-lm(cbind(Moral_DIL, Moral_SCA)~SleepQuantCro, Data_Study6_Wide)
QuantAcuLMS6<-lm(cbind(Moral_DIL, Moral_SCA)~SleepQuantAcu, Data_Study6_Wide)
```

**Extract coefficients (F test and p-values) from multivariate regression models **
```{r}
out <- car:::print.Anova.mlm
body(out)[[16]] <- quote(invisible(tests))
body(out)[[15]] <- NULL

#Chronic Sleep Quality
FQualCroS6<-round(do.call(rbind, out(Anova(QualCroLMS6, test.statistic="Pillai")))[3], digit=2)
pQualCroS6<-  round(ifelse(do.call(rbind, out(Anova(QualCroLMS6, test.statistic="Pillai")))[6]*4<.99, do.call(rbind, out(Anova(QualCroLMS6, test.statistic="Pillai")))[6]*4, .99), digit=2)

#Acute Sleep Quality
FQualAcuS6<-round(do.call(rbind, out(Anova(QualAcuLMS6, test.statistic="Pillai")))[3], digit=2)
pQualAcuS6<-  round(ifelse(do.call(rbind, out(Anova(QualAcuLMS6, test.statistic="Pillai")))[6]*4<.99, do.call(rbind, out(Anova(QualAcuLMS6, test.statistic="Pillai")))[6]*4, .99), digit=2)

#Chronic Sleep Quantity
FQuantCroS6<-round(do.call(rbind, out(Anova(QuantCroLMS6, test.statistic="Pillai")))[3], digit=2)
pQuantCroS6<-  round(ifelse(do.call(rbind, out(Anova(QuantCroLMS6, test.statistic="Pillai")))[6]*4<.99, do.call(rbind, out(Anova(QuantCroLMS6, test.statistic="Pillai")))[6]*4, .99), digit=2)

#Acute Sleep Quantity
FQuantAcuS6<-round(do.call(rbind, out(Anova(QuantCroLMS6, test.statistic="Pillai")))[3], digit=2)
pQuantAcuS6<-  round(ifelse(do.call(rbind, out(Anova(QuantAcuLMS6, test.statistic="Pillai")))[6]*4<.99, do.call(rbind, out(Anova(QuantAcuLMS6, test.statistic="Pillai")))[6]*4, .99), digit=2)

```

**Create datasets to display regression summary in plots**
```{r}
ResumQualCroS6<- paste0("F=",FQualCroS6,",","p=",pQualCroS6)
ResumQualAcuS6<- paste0("F=",FQualAcuS6,",", "p=",pQualAcuS6)
ResumQuantCroS6<- paste0("F=",FQuantCroS6,",","p=",pQuantCroS6)
ResumQuantAcuS6<- paste0("F=",FQuantAcuS6,",","p=",pQuantAcuS6)

annotationQualCroS6 <- data.frame(x = 14.5, y = 2.5,  label = ResumQualCroS6)
annotationQualAcuS6 <- data.frame(x = 16.5, y = 2.5,  label = ResumQualAcuS6)
annotationQuantCroS6 <- data.frame(x =7, y = 2.5,  label = ResumQuantCroS6)
annotationQuantAcuS6 <- data.frame(x = 7, y = 2.5,  label = ResumQuantAcuS6)

annotationS6<-cbind(
  rbind(annotationQualCroS6, 
        annotationQualAcuS6, 
        annotationQuantCroS6, 
        annotationQuantAcuS6),
  SleepType=c(
        "Quality of Chronic Sleep", 
        "Quality of Acute Sleep", 
        "Quantity of Chronic Sleep", 
        "Quantity of Acute Sleep"))
```


**Prepare data for plots**
```{r}
Data_PlotS6<- Data_Study6_Wide %>%
  pivot_longer(
    cols=c(SleepQualCro, SleepQualAcu, SleepQuantCro, SleepQuantAcu),
    names_to="SleepType") %>%
  rename("SleepValue"=value) %>%
  mutate(
    SleepLength=case_when(
      SleepType=="SleepQualCro" | SleepType=="SleepQuantCro"~"Chronic",
      SleepType=="SleepQualAcu" | SleepType=="SleepQuantAcu"~"Acute"),
    SleepQuanthist=case_when(
      SleepType=="SleepQualCro" | SleepType=="SleepQualAcu"~"Sleep Quality",
      SleepType=="SleepQuantCro" | SleepType=="SleepQuantAcu"~"Sleep Quantity"),
    MoralZ_DIL=scale(Moral_DIL, center = TRUE, scale = TRUE),
    MoralZ_SCA=scale(Moral_SCA, center = TRUE, scale = TRUE))

Data_PlotS6$SleepType<-dplyr::recode(Data_PlotS6$SleepType, 
        "SleepQualCro" = "Quality of Chronic Sleep",
        "SleepQualAcu" = "Quality of Acute Sleep",
        "SleepQuantCro" = "Quantity of Chronic Sleep",
        "SleepQuantAcu" = "Quantity of Acute Sleep")

Data_MoralS6<- Data_Study6_Wide %>%
  pivot_longer(
    cols=c(Moral_DIL, Moral_SCA),
    names_to="Outcome_moral") %>%
  rename("MoralValue"=value)

Data_MoralS6$Outcome_moral<-dplyr::recode(Data_MoralS6$Outcome_moral,
        "Moral_DIL" = "Dilemmas",
        "Moral_SCA" = "Scale")

Data_ScatterS6<- Data_PlotS6 %>%
  pivot_longer(
    cols=c(MoralZ_DIL, MoralZ_SCA),
    names_to="Outcome2") %>%
  rename("MoralValue2"=value)
Data_ScatterS6$Outcome<-dplyr::recode(Data_ScatterS6$Outcome, 
        "MoralZ_DIL" = "Dilemmas",
        "MoralZ_SCA" = "Scale")

```

**N in each sleep quantity category**
```{r}
Data_Study6_Wide$SleepQuantCroR<-round(Data_Study6_Wide$SleepQuantCro)
Data_Study6_Wide$SleepQuantAcuR<-round(Data_Study6_Wide$SleepQuantAcu)

Dist.Quantity.ChronicS6<-Data_Study6_Wide %>% 
    dplyr::group_by(SleepQuantCroR) %>% 
      summarise(
        N=n()) %>% 
          spread(SleepQuantCroR, N) %>% 
  as.data.frame()
row.names(Dist.Quantity.ChronicS6)<-"Quantity Chronic"

Dist.Quantity.AcuteS6<-Data_Study6_Wide %>% 
    dplyr::group_by(SleepQuantAcuR) %>% 
      summarise(
        N=n()) %>% 
          spread(SleepQuantAcuR, N) %>% 
  as.data.frame()
row.names(Dist.Quantity.AcuteS6)<-"Quantity Acute"

bind_rows(Dist.Quantity.AcuteS6, Dist.Quantity.ChronicS6)

```

## Summary of Study 6 results 

**Put results in a table**
```{r}
SleepMarker<-c("Quality Chronic","Quality Acute","Quantity Chronic","Quantity Acute")
FS6<-c(FQualCroS6,FQualAcuS6,FQuantCroS6,FQuantAcuS6)
pvalS6<-c(pQualCroS6,pQualAcuS6,pQuantCroS6,pQuantAcuS6)
NS6<-c(length(QualCroLMS6$fitted.values)/2,
     length(QualAcuLMS6$fitted.values)/2,
     length(QuantCroLMS6$fitted.values)/2,
     length(QuantAcuLMS6$fitted.values)/2)
ResultsStudy6<-data.frame("Sleep Indicator"=SleepMarker, "F-test"=FS6, "p values"=pvalS6, "N"=NS6)
gt(ResultsStudy6)
```

## Plots of Study 6 results

**Plot distribution for each sleep indicator**
```{r}
DistQualityS6<-ggplot(Data_PlotS6, aes(x=SleepValue, fill=factor(SleepLength))) + 
  geom_density(alpha=0.5, size=0.5,adjust = 2) + 
  scale_fill_manual(values=c("#193B94", "#BDCAEE")) +
  theme_bw() + 
  ylab("Density") + xlab("") +
  facet_wrap(~factor(SleepQuanthist), scale="free_x") + 
  guides(fill=guide_legend("Sleep Length")) +
  theme(
    axis.title.y = element_text(size = 11, hjust = 0.5, face="bold"),
    axis.title.x = element_text(face="bold", size = 11, hjust = 0.5),
    legend.position="top",
    legend.title = element_text(colour="black", size=10, face="bold")) 
DistQualityS6
```

**Plot distribution for the scores to the dilemmas and moral scale**
```{r}
DistMoralS6<-ggplot(Data_MoralS6, aes(x=MoralValue, fill=factor(Outcome_moral))) + 
  geom_density(alpha=0.5, size=0.5,adjust = 2) + 
  theme_bw() + 
  ylab("Density") + xlab("Moral Scale") +
  facet_wrap(~factor(Outcome_moral), scale="free") +
  guides(fill="none") +
  theme(
    axis.title.y = element_text(size = 11, hjust = 0.5, face="bold"),
    axis.title.x = element_text(face="bold", size = 11, hjust = 0.5))
  
DistMoralS6
```


**Scatterplots**
```{r}
ggplot(Data_ScatterS6, aes(x=SleepValue, y=MoralValue2, 
                           color=Outcome2, fill=Outcome2)) + 
       geom_smooth(method="lm")+
      geom_point(alpha=0.2)+
       facet_wrap(~factor(SleepType), scales="free_x") +
       theme_bw() + ylab("Utilitirianism") + xlab("") + 
       theme(axis.title.y = element_text(size = 11, hjust = 0.5, face="bold"), 
             axis.title.x = element_text(face="bold", size = 11, hjust = 0.5)) +
       guides(size=FALSE, colour=FALSE) + 
       scale_fill_manual(values=c("red","#193B94"))+
       scale_color_manual(values=c("red","#193B94"))+
       geom_label(data=annotationS6, aes( x=x, y=y, label=label), 
                  color="black",  size=3.5 , angle=45, alpha=7/10, 
                  inherit.aes = FALSE)
```